---
title: "Ordinal regression models"
output: html_notebook
---

Eine kurze uebersicht ueber die verschiedenne ordinalen regressionsmodelle.
wir haben mehrere ordinale outcome variablen in den analysen. manchmal sind praediktoren kategorisch, ordinal, oder metrisch.

```{r}
# examples with brms

load("../data/df_crq.RData")
library(brms)
library(tidyverse)
```

## intercept only model

```{r}
fit <-
  brm(data = df_crq,
      family = cumulative(probit), #cumulative probit is one way to model ordinal outcomes
      jcha_1_work ~ 1,
      prior = c(prior(normal(0, 4), class = Intercept))) # example sets prior but i dont know the details..

summary(fit)
```
given 5 CRQ response cateogies, we have 4 estimated thresholds. The latent distribution
that is modelled has mu = 0, sigma = 1.
```{r}
pp_check(fit)

```

## metric predictor model

```{r}

# standardize X
df_crq <-
  df_crq %>% 
  mutate(lear_s = scale(lear))

# fit with metric predictor. Book reminds to think clearly about priors.
fit23.9 <-
  brm(data = df_crq,
      family = cumulative(probit),
      jcha_1_work ~ 1 + lear_s,
      prior = c(prior(normal(0, 4), class = Intercept),
                prior(normal(0, 4), class = b)),
      iter = 3000, warmup = 1000, chains = 4, cores = 4,
      seed = 23)

summary(fit23.9)
```

0.26 is the estimate, which is here a standardized regression estimate (beta).

## ordinal predictor

see http://paul-buerkner.github.io/brms/articles/brms_monotonic.html
Ordinal predictors can be seen as monotonic predictors with unequal distances between categories.
To model this, brms uses two parameters: "b takes care of the direction and size of the effect similar to an ordinary regression parameter. If the monotonic effect is used in a linear model, b can be interpreted as the expected average difference between two adjacent categories of the ordinal predictor. An additional parameter vector, ζ (Zeta), estimates the normalized distances between consecutive predictor categories which thus defines the shape of the monotonic effect."
Monotonous predicted are used with the `mo()` argument.

```{r}
df_crq <- df_crq %>%
  mutate(edu = fct_collapse(education_de,
                            low = c("Obligatorische Schulpflicht",
                                     "Mittelschule (Gymnasium, Abitur, Handelsschule, Fachmittelschule)"),
                            high = c("Master (Universität / Fachhochschule)", "Doktorat"))) %>% 
  mutate(edu = as.ordered(edu))
```


```{r}
fit_mo <-
  brm(data = df_crq,
      family = cumulative(probit),
      jcha_1_work ~ 1 + mo(edu),
      prior = c(prior(normal(0, 4), class = Intercept)),
      iter = 2000, warmup = 1000, chains = 4, cores = 4,
      seed = 23)

summary(fit_mo)
```

Priors are complex for monotonous functions, see the linked article.
The output lists b and the ζ is shown in the simplex parameters which delineates the thresholds between the categories of the predictor (summing up to 1).

Extensions for random effect models are also given there.

